---
title: "Faye’s Week 4 Homework"
author: "Faye Harwell"
date: "September 27, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Homework for Week 4- Let's do some countin' of some Titi Monkeys

### So, we have an expected occurence of 8 monkey sightings (jk hearings) from 5am to 7am... primatologists may or may not be masochistic doing work at 5am when the sun rises...  
 
### Regardless, that means that λ is equal to 8
 


### Question 1: What is the probability that she will hear more than 8 calls during any given session?

```{r}
1-ppois(q=8,lambda = 15)
```

### Answer: 0.407452658562409

### Question 2: What is the probability that she will hear no calls in a session?

```{r}
ppois(q=0, lambda = 15)
```

### Question 3: What is the probability that she will hear exactly 3 calls in a session?
```{r}
ppois(q=3, lambda = 15)
```

### Question 4: Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30

### Answer: See Plot Below

```{r}
x <- 0:30
l = 15
probset <- dpois(x = x, lambda = l)
barplot(probset, names.arg = x, space = 0, xlab = "Number of Calls Counted", ylab = "Pr(X = x)", main = "Probability Mass Function")
```

### Question 5: Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).

```{r}
hist_of_sim <- rpois(104, lambda = 15)
hist(hist_of_sim, xlab = "Number of Calls", ylab = "Frequency of Call Amounts", xlim= c(0,30), main = "Histogram of Daily Call Counts")

hist_of_sim
```
