---
title: "Faye Harwell- Zombie Apocolapse Homework"
author: "Faye Harwell"
date: "September 28, 2017"
output: html_document
---


# ZOMBIE Homework... we got some killin' to do!

### To get started, load your badass dataset: 

```{r}
library(curl)
f <- f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall17/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
d
```


### Question 1: Calculate dem means... what doooo you mean? 
```{r}
mean(d$height)->avg_height
avg_height
```
    
```{r}
mean(d$weight)->avg_weight
avg_weight
```
```{r}
mean(d$zombies_killed)->avg_zombieskilled
avg_zombieskilled
```

```{r}
mean(d$years_of_education)->avg_years_of_education
avg_years_of_education
```

```{r}
population_size <-length(d$id)
population_size
```

### The fun part is computing variance by hand... everyone enjoys that..

```{r}
var_height<-(sum((d$height-avg_height)^2)/(1000))
var_height
```

```{r}
var_weight<-(sum((d$weight-avg_weight)^2)/(1000))
var_weight
```

```{r}
var_zombieskilled<-(sum((d$zombies_killed-avg_zombieskilled)^2)/(1000))
var_zombieskilled
```

```{r}
var_years_of_education<-(sum((d$years_of_education-avg_years_of_education)^2)/(1000))
var_years_of_education
```

### Let's pull it all together... actually we are going to squareroot the sh*t out of this stuff

```{r}
sd_height <- sqrt(var_height)
sd_height
```

```{r}
sd_weight <- sqrt(var_weight)
sd_weight
```

```{r}
sd_zombieskilled <- sqrt(var_zombieskilled)
sd_zombieskilled
```

```{r}
sd_years_of_education <- sqrt(var_years_of_education)
sd_years_of_education
```

## Question 2: G-G Plotting... any thing to do with G-G rubbing.. Hopefully, not...

### Boxing a plot of males and females for Height

```{r}
library(ggplot2)
```

```{r}
ggplot(aes(y = height, x = gender), data = d) + ylab("Height (inches)") + xlab("Gender") +geom_boxplot(fill= "turquoise")->boxplot_height
boxplot_height
```

```{r}
ggplot(aes(y = weight, x = gender), data = d) +ylab("Weight (Pounds)") + xlab("Gender") + geom_boxplot(fill= "mediumorchid")->boxplot_weight
boxplot_weight
```

```{r}
ggplot(aes(y = zombies_killed, x = gender), data = d) + ylab("Number of Zombies Killed") + xlab("Gender") + geom_boxplot(fill= "limegreen")->boxplot_zombieskilled
boxplot_zombieskilled
```

```{r}
ggplot(aes(y = years_of_education, x = gender), data = d) + ylab("Number of Years of Education") + xlab("Gender") + geom_boxplot(fill= "cornflowerblue")->boxplot_education
boxplot_education
```

## Question 3: More G-G rubbing... I mean plotting. This time around do some scattering of the plot (aka a scatterplot!)

#### Both scatterplots show a positive relationship/correlation (although I have not gone ahead and tested whether it is significant). This means that as you get older, you are likely to be heavier and taller... I like when data is straight forward and makes sense!
```{r}
ggplot(d, aes(age, weight)) + xlab("Age (years)") + ylab("Weight (pounds)")+
  geom_point(shape = 16, size = 1, show.legend = FALSE, colour = ("deeppink1")) + theme_classic()
```

## Question 4: Being normal is vastly overrated.... you could be anything... Poison, Bernoulli, Beta, and the list goes on and on! Anyways, go ahead and check for normality using Q-Q Plots and histograms

```{r}
ggplot(d, aes(age, height)) + xlab("Age (years)") + ylab("Height (inches)")+
  geom_point(shape = 16, size = 1, show.legend = FALSE, colour = ("mediumspringgreen")) + theme_classic()
```

```{r}
qqnorm(d$height, cex=0.5, main="QQ Plot for Height")
qqline(d$height, col="pink")
hist(d$height, main="Height of Apocolapse Survivors", xlab="Height (inches)", ylab="Frequency", col="lightblue")
```
### In my expert opinion, height is looking pretty darn normal. In the Q-Q plot, you see a very nice straight line plotted for sample quantiles plotted against theoretical quantiles. Likewise, the histogram of the frequency of heights is bell-shaped. 

```{r}
qqnorm(d$weight, cex=0.5, main="QQ Plot for Weight")
qqline(d$weight, col="lightblue")
hist(d$weight, main="Weight of Apocolapse Survivors", xlab="Weight (inches)", ylab="Frequency", col="pink")
```

### Again, very normal looking. Both in the histogram and the Q-Q plot you see the points being normally distributed (i.e. straight line for sample quantiles plotted against theoretical quantiles and nice bell-shaped curve)

```{r}
qqnorm(d$zombies_killed, cex=0.5, main="QQ Plot for Number of Zombies Killed")
qqline(d$zombies_killed, col="pink")
hist(d$zombies_killed, main="Number of Zombies Killed by Survivors", xlab="Number of Zombies Killed", ylab="Frequency", col="lightblue")
```

### Both the Q-Q plot and the histogram showing the number of zombies killed by survivors do not follow a normal distribution. The histogram shows a right skew distribution. I predict that this may be a poisson distribution as it is highly skewed. 

```{r}
qqnorm(d$years_of_education, cex=0.5, main="QQ Plot for Years of Education")
qqline(d$years_of_education, col="orange")
hist(d$years_of_education, main="Education of Apocolapse Survivors", xlab="Number of Years of Education", ylab="Frequency", col="purple")
```

### Both the Q-Q plot and the histogram showing the number of years of education of survivors do not follow a normal distribution. The histogram shows a right skew distribution. I predict that this may be a poisson distribution as it is highly skewed. 

## Question 5: Random Sampling!

```{r}
library(dplyr)
sample(d$id, size= 30, replace = FALSE, prob = NULL)-> random_rows
d %>% slice(random_rows)-> random30
```

```{r}
library(dplyr)
d[sample(nrow(d),30),]
```

```{r}
random30
```

### NOW, instead of doing these god forsaken equations again... copy from above Question 1's work (Standard Deviation & Mean done out by hand)

```{r}
mean(random30$height)->avg_height30
avg_height30
```
    
```{r}
mean(random30$weight)->avg_weight30
avg_weight30
```

```{r}
mean(random30$zombies_killed)->avg_zombieskilled30
avg_zombieskilled30
```

```{r}
mean(random30$years_of_education)->avg_years_of_education30
avg_years_of_education30
```


### COPIED: The fun part is computing variance by hand... everyone enjoys that..

```{r}
var_height30<-(sum((random30$height-avg_height30)^2)/(30))
var_height30
```

```{r}
var_weight30<-(sum((random30$weight-avg_weight30)^2)/(30))
var_weight30
```

```{r}
var_zombieskilled30<-(sum((random30$zombies_killed-avg_zombieskilled30)^2)/(30))
var_zombieskilled30
```

```{r}
var_years_of_education30<-(sum((random30$years_of_education-avg_years_of_education30)^2)/(30))
var_years_of_education30
```

### COPIED: Let's pull it all together... actually we are going to squareroot the sh*t out of this stuff

```{r}
sd_height30 <- sqrt(var_height30)
sd_height30
```

```{r}
sd_weight30 <- sqrt(var_weight30)
sd_weight30
```

```{r}
sd_zombieskilled30 <- sqrt(var_zombieskilled30)
sd_zombieskilled30
```

```{r}
sd_years_of_education30 <- sqrt(var_years_of_education30)
sd_years_of_education30
```

### Even better, you get to do standard error calculations... aren't you a lucky ducky

```{r}
se_height30<-sd_height30/sqrt(30)
se_height30
```
```{r}
se_weight30<-sd_weight30/sqrt(30)
se_weight30
```
```{r}
se_zombieskilled30<-sd_zombieskilled30/sqrt(30)
se_zombieskilled30
```

```{r}
se_years_of_education30<-sd_years_of_education30/sqrt(30)
se_years_of_education30
```

### Lucky Ducky, I got more news for you- you get to do confidence intervals.

```{r}
c(avg_height30-2*se_height30, avg_height30+2*se_height30)
```
```{r}
c(avg_weight30-2*se_weight30, avg_weight30+2*se_weight30)
```
```{r}
c(avg_zombieskilled30+1.96*(avg_zombieskilled30/30), avg_zombieskilled30-1.96*(avg_zombieskilled30/30))
```

```{r}
c(avg_years_of_education30+1.96*(avg_years_of_education30/30), avg_years_of_education30-1.96*(avg_years_of_education30/30))
```

## Question 5: Random sampling... again... 99 more times to be precise...

### Hmmm maybe replicate () will be helpful... or not. 

```{r}
replicated_99 <- replicate(99,d[sample(nrow(d),30),])
replicated_99
```
### Faye, remember that you have terrible naming abilities and you named your 'height' variables hah and haha

```{r}
replicated_99[5,]-> heights99
for (i in 1:99){
  hah[i] <- mean(heights99[[i]])
}
hah
```

```{r}
mean(hah)-> haha
haha
hist(hah, col="magenta", xlab= "Height", main= NULL)
```

### Do better names this time round (good thing you do this like 4 more times)

### This is for Weight
```{r}
replicated_99[6,]-> weights99
for (i in 1:99){
  lala[i] <- mean(weights99[[i]])
}
lala
```

```{r}
mean(lala)-> lalala
lalala
hist(lala, col="blue", xlab= "Weight", main= NULL)
```

### This is for Number of Zombies Killed
```{r}
replicated_99[7,]-> zombieskilled99
hehe <- 0
for (i in 1:99){
  hehe[i] <- mean(zombieskilled99[[i]])
}
hehe
mean(hehe)-> hehehe
hehehe
hist(hehe,col="lightgreen", main=NULL, xlab= "Number of Zombies Killed")
```

### This is for Number of Years of Education

### This is for Number of Zombies Killed
```{r}
replicated_99[8,]-> yearsofeducation99
dumdum <- 0
for (i in 1:99){
  dumdum[i] <- mean(yearsofeducation99[[i]])
}
dumdum
mean(dumdum)-> dumdumdum
dumdumdum
hist(dumdum, col="lightblue", xlab= "Years of Education", main= NULL)
```